Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-08-13 cosmic_voids.tex
Captioning table 1 and figure 3 (visual impression). Finishing density-based web finder

%-------------------------------------------------------------------------
\subsection{The tidal web finder (T-web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\subsection{The velocity web finder (V-web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

@@

  \captionof{figure}{\small In this figure is shown the distribution of the
  fractional anisotropy (left panel) and density field (right panel) with 
  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
  lines. V-web, blue lines) as calculated over all the cells of the grid.
  Thick central lines correspond to the median of the distribution and 
  coloured regions to the $50\%$ of the cells, delimited by quartiles 
  $Q_1$ and $Q_3$.}

@@

  \captionof{figure}{\small Distribution of the fractional anisotropy 
  (upper panel) and density field (lower panel) with respect to the 
  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
  blue lines) as calculated over all the cells of the grid. Thick central 
  lines correspond to the median of the distribution and coloured regions 
  to the $50\%$ of the cells, delimited by quartiles $Q_1$ and $Q_3$.}

@@

%-------------------------------------------------------------------------
\subsection{Density-based web finder}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

In order to compare our tracing field based on the fractional anisotropy,
we define here a very basic approach for environmental finding based on 
three thresholds set in the density field. Although the density field is
a key quantity for understanding the large-scale Universe, the filamentary 
structure of the Cosmic Web is poorly traced by it (see figure 
\ref{fig:FA_field}).

%.........................................................................
%Table with volume filling fraction
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{c  c  c  c c} \hline\hline
	\textbf{Volume}					&				&\textbf{Scheme}& \\
	\textbf{Filling}				&				&				&					  &  \textbf{Threshold} \\ 
	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

@@

@@

%.........................................................................
%FIGURE 4: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_density.pdf}

  \captionof{figure}{\small In left panels is shown the visual impression 
  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
  defined types of environment, where voids corresponds to white zones, 
  sheets to gray, filaments to dark gray and finally knots to black regions. 
  In the right panels is shown the fractional anisotropy field for the same 
  slide of the simulation and for each web schemes, where black regions 
  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
  degeneration of low values of FA for knots and central regions of voids, 
  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
  and highly planar sheets. Thin dark red curves correspond to contours of
  $FA=0.95$, which is approximately the transitional FA between voids and
  other cosmological regions.}

  \label{fig:FA_field}
  \vspace{0.1 cm}

>>>>

%-------------------------------------------------------------------------
\subsection{The tidal web (T-web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\subsection{The velocity web (V-web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

@@

  \captionof{figure}{\small Volume Filling Fraction for each type of 
  environment with respect to the chosen threshold $\lambda_{th}$ for both
  web schemes (T-web, left panel. V-web, right panel). For each case, the 
  threshold value is chosen such that the fractional anisotropy along the 
  void-sheet boundaries has a value of $FA=0.95$.}

@@

  \captionof{figure}{\small Distributions of fractional anisotropy 
  (left panel) and density field (right panel) with respect to the 
  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
  blue lines) as calculated over all cells of the grid. Thick central 
  lines correspond to the median and filled regions to the $50\%$ of 
  the distribution.}

@@

%-------------------------------------------------------------------------
\subsection{The density-based web finder}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

Although the density field is a key quantity for understanding the 
large-scale Universe, the filamentary structure of the Cosmic Web is 
poorly traced by it (see e.g. figure \ref{fig:FA_field}). In order to 
compare our new proposal about the the fractional anisotropy as a tracer 
field of voids, we define a very basic approach for environmental finding 
based on three thresholds of the density field.

%.........................................................................
%Table with volume filling fraction
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{c  c  c  c c} \hline\hline
	\textbf{Volume}  &				&\textbf{Scheme}& \\
	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
	\textbf{Fraction}&\textbf{T-web}&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
	Sheets		     &	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	      &	$0.60$				\\
	Filaments		 &	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 		  &	$8.82$				\\
	Knots			 &	$0.75\%$	&	$1.22\%$	&	$0.98\%$  		  &	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small VFF for each type of environment and for each
  web scheme. VFF for the density-based scheme are defined as the 
  arithmetic mean of the T-web and the V-web. The last column corresponds 
  to the threshold values in the density field in order to obtain the 
  required VFF. Note there is not any value associated to knots as there 
  is not a higher order environment.}

@@

%.........................................................................
%FIGURE 4: FA and vissual impression
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \vspace{0.1 cm}  
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_density.pdf}

  \captionof{figure}{\small Left panels show the visual impression of the 
  Cosmic Web for each web scheme (T-web, upper panels. V-web, middle 
  panels. Density, lower panels). It can be noticed each environment 
  sketched such that voids corresponds to white, sheets to gray, filaments 
  to dark gray and knots to black regions. Right panels show the fractional 
  anisotropy field for the same slide of the simulation and for each web 
  scheme. Black regions correspond to the maxim value, i.e. FA$=1$, while 
  white and light yellow regions to FA$=0$. It is worth noting the 
  degeneration of low values of FA for knots and central regions of voids, 
  thus indicating a high isotropy for both processes. In the same way, high 
  values of FA (FA $\lesssim 1$) are consistent the anisotropic geometry 
  exhibited by filaments and very flat sheets.}

  \label{fig:FA_field}

\end{figure*}
%.........................................................................

In next section we shall describe an alternative approximation to select 
the threshold value $\lambda_{th}$, and as will be shown, one of its main 
advantages is the similar volume filling fraction (VFF) of each 
environment as compared between both web schemes. Using this result, we 
propose here a heuristic classification of the Cosmic Web based on 
three density thresholds assigned to each boundary (i.e. void-sheet, 
sheet-filament and filament-knot)\footnote{The progressive sequence 
void-sheet-filament-knot along any path in the Cosmic Web should be always
satisfied as each used field is smoothed. For instance, it should not be 
possible to find a knot-type cell abutting another sheet or void-type 
cell.} such that the corresponding VFF values are similar to the values 
obtained for the T-web and the V-web, specifically they are defined 
to be the arithmetic mean of both schemes.

@@
